The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2025-11-02 SIGMA/SIGMA_submission/borel_reg_submission.tex
Clarify section reference; add missing period
Polish acknowledgements

Using the properties of the Borel transform acting on trans-mononials \ref{sec:action_transseries}~we~get 
\begin{equation*}
\begin{split}
\series{\iota}_a & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}
\end{split}
\end{equation*}
We know from the definition of $\varepsilon$ that $\left|b_n^a\right| \varepsilon^n \lesssim 1$, thus we deduce that $\series{\iota}$ has a finite radius of convergence. This ends the proof of part~\ref{part-2-prf}.

@@

We thank Fondation Mathématique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.

We thank Fr\'{e}d\'{e}ric Fauvet, Maxim Kontsevich, Andrew Neitzke, and David Sauzin for fruitful discussions and suggestions. We would like to thank the anonymous referees for many helpful suggestions.

>>>>

Using the properties of the Borel transform acting on trans-mononials (Section~\ref{sec:action_transseries}) we get
\begin{equation*}
\begin{split}
\series{\iota}_a & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}\,.
\end{split}
\end{equation*}
We know from the definition of $\varepsilon$ that $\left|b_n^a\right| \varepsilon^n \lesssim 1$, thus we deduce that $\series{\iota}$ has a finite radius of convergence. This ends the proof of part~\ref{part-2-prf}.

@@

We thank Fondation Math\'{e}matique Jacques Hadamard for supporting the visit of the second author at IH\'{E}S, under the program \textit{Junior Scientific Visibility}.

We thank Fr\'{e}d\'{e}ric Fauvet, Maxim Kontsevich, Andrew Neitzke, and David Sauzin for fruitful discussions and suggestions. We thank the referees for their careful reading, thoughtful comments, and useful references.

### 2025-11-02 SIGMA/borel-regularity-SIGMA.tex
Polish acknowledgements

We thank Fondation Mathématique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.

We thank Fr\'{e}d\'{e}ric Fauvet, Maxim Kontsevich, Andrew Neitzke, and David Sauzin for fruitful discussions and suggestions.
%
\section{Historical context}\label{sec:historical-context}
%
\subsection{Borel regularity as a good approximation condition}
Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials. Watson showed a century ago \cite[Part II, Section 9]{watson2} that a function $\Phi$ is Borel regular whenever its asymptotic expansion for large $|z|$ is uniformly $1$-Gevrey-asymptotic in an obtuse-angled sector at infinity (see Definition~\ref{def:unif-gevrey-asymp}).

>>>>

We thank Fondation Math\'{e}matique Jacques Hadamard for supporting the visit of the second author at IH\'{E}S, under the program \textit{Junior Scientific Visibility}.

We thank Fr\'{e}d\'{e}ric Fauvet, Maxim Kontsevich, Andrew Neitzke, and David Sauzin for fruitful discussions and suggestions. We thank the referees for their careful reading, thoughtful comments, and useful references.
%
\section{Historical context}\label{sec:historical-context}
%
\subsection{Borel regularity as a good approximation condition}
Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials. Watson showed a century ago \cite[Part II, Section 9]{watson2} that a function $\Phi$ is Borel regular whenever its asymptotic expansion for large $|z|$ is uniformly $1$-Gevrey-asymptotic in an obtuse-angled sector at infinity (see Definition~\ref{def:unif-gevrey-asymp}).
